NDNS multilevel LCA CW2CB2 or CW2CB3

### 2018-08-18 paper/Chapters/Chapter4.tex
before go to chaed party

Secondly, the classification of individuals to latent carbohydrate eating classes are defined by maximum posterior probability assignment rule. This approach assigns individuals to the class for which they have the highest posterior probability of membership \parencite{nagin2005group}.

\begin{itemize}
	\item We used the maximum probability rule and ignored that these are just probabilities. but inclusive MLCA might perform better.
	\item we do not have the information of whether the participants were doing job that requires shift work.
	\item dietary report under estimation
	\item findings may not be generalizable to populations from other countries.
\end{itemize}

>>>>

Secondly, the classification of individuals to latent carbohydrate eating classes were defined by maximum posterior probability assignment rule. This approach assigns individuals to the class for which they have the highest posterior probability of membership \parencite{nagin2005group}. The other approach is multiple pseudo-class draws \parencite{wang2005residual}, which was proposed in attempt to account for uncertainty in class assignment. However, the maximum probability rule is still believed to be able to minimize the number of incorrect assignments \parencite{goodman20071}. A Monte Carlo simulation study \parencite{bray2015eliminating} also demonstrated that maximum probability assignment is less biased than multiple pseudo-class draws. Moreover, this simulation study also found that an inclusive LCA (i.e. LCA with covariates) would perform better, and reduce bias. Since whether this advantage can be extended to MLCA in the current project is unknown, and also due to the reason that the associations between the latent classes and distal outcomes (hypertension, and BMI) in our analyses were mostly still under exploration, therefore, the model for LCA with covariates can never be well-known before our analyses. Thus, as a first step, also given the complexity of the NDNS RP dataset itself, we chose to conduct the MLCA modellings without any covariate in either day level or individual level models. Future studies may be advised to consider incorporating other predictors in the MLCA models to see whether the classifications in both levels can be improved or not.

Thirdly, information regarding the detailed occupations of the participants was not available, so we could not exclude those who had a shift work involving night work. But considering that completing a 4-consecutive-day food diary would be a large burden for the participants, those had a shift work involving night work might possibly performed relatively lower compliance and could not complete their diary for at least 3 days. But this cannot be verified in the NDNS RP dataset. If people working with shift work were included in the NDNS RP sample, the classification in both levels as well as their associations with either hypertension or BMI would be biased. Furthermore, under-reporting is also a concern in the diaries collected. To evaluate the influence of under-reporting in the NDNS RP sample, study team of NDNS RP conducted doubly labelled water (DLW) sub-study within the survey. The details of this sub-study can be accessed from the Appendix X of the Official Reports provided by Public Health England \parencite{bates2014national,roberts2018national,NDNSofficial}.

\begin{itemize}
	\item dietary report under estimation
	\item findings may not be generalizable to populations from other countries.
\end{itemize}
